Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps

### 2018-11-21 IPCO format/binaryFDT.tex
Dom2IP fixed

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}

@@

The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$. The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$. 
\iffalse{
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\label{domtoIPalg}
	\caption{The DomToIP algorithm}
\end{algorithm}
}\fi
We prove that indeed $(x^{(t)},y^{(t)})\in S$.

@@

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the DomToIP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

>>>>

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $(x,y)\in \dom(P)$, there is an algorithm (the Dom2IP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}

@@

The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$. The Dom2IP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$. 
\iffalse{
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\label{domtoIPalg}
	\caption{The Dom2IP algorithm}
\end{algorithm}
}\fi
We prove that indeed $(x^{(t)},y^{(t)})\in S$.

@@

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the Dom2IP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
